### 2014-11-18 poster/poster.tex
draft poster as printed

These data are summarized graphically in figures \ref{fg:hist} and
\ref{fg:timeseries} below. From the histogram, we see what looks to be
a Poisson distribution with over dispersion. From the timeseries plot,
we see that there is a clear yearly pattern, as well as a weekly
pattern.

@@

\section{Model Specification}
Because over dispersion was evident in the counts, we chose to fit a
negative binomial model. This model includes the following variables,
and was fit using the \texttt{pscl::glm.nb()} function in R.

@@

\section{Model Fit and Diagnostics}

As the actual-versus-predicted plot below shows, the model is a
reasonably good fit. However, we note several outliers falling far
from the $y=x$ line, perhaps indicating some other unaccounted source
of variation in the dataset.

@@

\subsection{Precipitation}
Similiarly, we see the strong negative effect of precipitation in our simulated
results.

>>>>

These data are summarized graphically in figures \ref{fg:hist} and
\ref{fg:timeseries} below. From the histogram, we see what
approximately looks to be a Poisson distribution with over dispersion.
From the timeseries plot, we see that there is a clear yearly pattern,
as well as a weekly pattern.

@@

\section{Model Specification}
Because over dispersion was evident in descriptive exploration of the
counts, we chose to fit a negative binomial model. This model includes
the following variables, and was fit using the \texttt{pscl::glm.nb()}
function in R.

@@

\newpage
\section{Model Fit and Diagnostics}

As the actual-versus-predicted plot below shows, the model is a
reasonably good fit. However, we note several outliers falling far
from the $y=x$ line, perhaps indicating some other unaccounted source
of variation in the dataset. For comparison, we also fit this model as
a Poisson model, however both the AIC and BIC were over six times as
large as in the negative binomial, indicating a much poorer fit.

@@

\subsection{Precipitation}
Similiarly, we see the strong negative effect of precipitation in our simulated
results. This corroborates our understanding of bicyclist aversion to rain.
